Doing Better Than UCT: \\ Rational Monte Carlo Sampling in Trees

### 2011-06-22 paper/rmcts/paper.tex
added grt algorithms

\begin{figure}[t]
\centering
\includegraphics[scale=0.64]{onelevel-64.pdf}
\caption{Simple regret in MAB: UCB vs. $\varepsilon$-greedy vs. UVB}
\label{fig:onelevel-64}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.64,trim=0pt 0pt 0pt 24pt,clip]{twolevel-64.pdf}
\caption{MCTS: UCT vs. UVT vs. VCT vs. Random}
\label{fig:twolevel-64}
\end{figure}

@@

\subsection{Simple regret in MAB}

\begin{figure}[t]
\centering
\includegraphics[scale=0.64,trim=0pt 0pt 0pt 0pt,clip]{onelevel-8-16-32-64.pdf}
\caption{Simple regret in MAB, varying number of arms}
\label{fig:onelevel-8-16-32-64}
\end{figure}

@@

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-factor=_8438.pdf}
  \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-nsamples=185.pdf}
  \end{minipage}
  \caption{The sailing domain, a smaller lake}
  \label{fig:sailing-8}
\end{figure}

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-factor=_5625.pdf}
  \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-nsamples=240.pdf}
  \end{minipage}
  \caption{The sailing domain, a larger lake}
  \label{fig:sailing-13}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.64]{onelevel-64.pdf}
  \caption{Simple regret in MAB: UCB vs. $\varepsilon$-greedy vs. Random}
  \label{fig:onelevel-64}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.64,trim=0pt 0pt 0pt 24pt,clip]{twolevel-64.pdf}
  \caption{MCTS: UCT vs. GRT vs. GCT vs. Random}
  \label{fig:twolevel-64}
\end{figure}

@@

@@

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-factor=_8438.pdf}
    {a. varying number of samples} 
 \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-nsamples=185.pdf}
    {b. varying exploration factor}
  \end{minipage}
  \caption{The sailing domain, a smaller lake}
  \label{fig:sailing-8}
\end{figure}

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-factor=_5625.pdf}
    {a. varying number of samples}
  \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-nsamples=240.pdf}
    {b. varying exploration factor}
  \end{minipage}
  \caption{The sailing domain, a larger lake}
  \label{fig:sailing-13}
\end{figure}
